\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2016-04-18 latex/UMEM_CoSim.tex
Added text content for lit review, massaging references, results discussion, etc

In order to address the deficiencies of the individual engines, the current effort described seeks to couple building and urban scale simulation. The research in this paper is part of an larger coupling effort in which various engines are connected and co-simulated to create a more comprehensive analysis of the urban scale \citep{Dorer:2013vt}. The target is the computational interface between the building energy model, using EnergyPlus, and the urban energy model using CitySim. An overview of the larger scope is shown in Figure \ref{fig:UMEM} and the context of the coupling task is shown as the interface between the City Energy Simulation (CES) model and the Building Energy Simulation (BES) model.

@@

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between simulation engines at various scales. Much of the initial co-simulation work is at the subsystem and building-scales. Previous studies have analyzed strong and loose coupling of engines at this scale \citep{Trcka:2010cr,Wetter:2011kh}. Coupling of building-scale simulation with urban-scale computational fluid dynamics (CFD) is attempted for modelling natural ventilation \citep{Zhang:2013vx} and to improve energy prediction \citep{Bouyer:2011eha}. EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program \citep{Yang:2012cr}. It was also coupled with simplified lumped parameter models in order to facilitate comparison with measured sensor data \citep{Martin:2015fj}. EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi}. 
% \subsection{Urban scale performance simulation}

\section{Methodology}\label{Methodology}
% A significant amount of the following methodology is developed in previous literature and is reiterated in this section in order to set the context for Section \ref{Implementation}. The previous published research is clearly outlined at the beginning of each subsection.

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.7]{figures/UMEM_Workflow}
\caption{Overview diagram of the coupling process including tools and outputs (adapted from \cite{thomas2014multiscale})}
\label{fig:OverallWorkflowProcess}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.7]{figures/UMEM_FMU_Overview}
\caption{Simulation information exchange between CitySim and EnergyPlus using FMI (adapted from \cite{thomas2014multiscale})}
\label{fig:FMUOverview}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1.0\textwidth]{figures/LWRCalc_Combined_V3}
  \caption{Comparison of the LWR components between a) Solo EnergyPlus and b) Coupled CitySim/EnergyPlus configuration (adapted from \citep{Miller:2015vk})
  \label{combinedLWR}}
\end{figure}

@@

The focus of the co-simulation process is that the performance of a targeted building is evaluated through solo and coupled methods. The HPI building on campus was chosen in this case study due to amount and quality of measured data available from the EMS for this building. The HPI building is indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded red.

@@

\subsection{Model development}
In order to perform a co-simulation of the targeted buildings, initially a CitySim model of the campus is developed. Through the workflow automation process, this geometry was converted into an EnergyPlus input file as seen in Figure \ref{fig:HPIcampus}. 
% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.

\begin{figure}[H]
\centering
\includegraphics[scale=0.2]{figures/HPI_Campus.png}
\caption{The HPI building modeled with OpenStudio for Sketchup.}
\label{fig:HPIcampus}
\end{figure}

@@

The measured and simulated data from both the co-simulation and EnergyPlus solo simulation was compared in order to create a realistic scenario for comparison. The calibration process was undertaken through a series of steps such as including local weather conditions for the simulation period and adding custom lighting schedules and power densities extracted from the measured data. The models were calibrated to the summer season (May-September) for cooling and the winter season (Jan-April and October to December) for heating. This approach was taken as the data quality for the measurements were deemed most accurate during the appropriate seasons. Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the simulations after the tuning process. Daily data was used to calculated goodness of fit to determine calibration success.

@@

After calibration, a comparison of co-simulation and solo EnergyPlus simulations are made. Figure \ref{fig:hpi_energyplusheating} illustates the difference in predicted heating energy consumption across the test year. A consistent offset exists across the time frame of days in January, the peak of the heating season. A more varied discrepancy across the heating months is noticed resulting and overall increase of heating prediction of 4.8\% due to co-simulation.

@@

For cooling, a more dramatic discrepancy can be seen between co-simulation and solo EnergyPlus. A 20.2\% decrease in predicted cooling energy is observed.

@@

\subsection{Campus case study 2: EPFL Quartier Nord}
Quartier Nord is a whole new quarter of the École Polytechnique Fédérale de Lausanne (EPFL) campus located at its northwest corner. This complex includes a Convention Centre with an auditorium with a maximum capacity of 3000 (seated) people, housing for 516 students, retail and service areas and a hotel. As a public space, this ensemble is organized around a main plaza (see Figure \ref{fig:quartier_nord_1}).

@@

Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information (see Figure \ref{fig:model_yang}).

@@

When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed.

@@

A 2.8\% increase in heating energy is observed.

@@

When focusing on solely on CitySim, a X\% decrease in cooling energy is observed.

@@

A 30.8\% decrease in heating energy is observed.

@@

@@

The authors would like to acknowledge the ETH Z\"urich Campus Facilities Department and the EPFL Real Estate and Infrastructure Department. This research was funded by the Competence Center in Energy and Mobility (CCEM) under the UMEM project.

>>>>

In order to address the deficiencies of the individual engines, the current effort described seeks to couple building and urban scale simulation. The research in this paper is part of an larger coupling effort in which various engines are connected and co-simulated to create a more comprehensive analysis of the urban scale \citep{Dorer:2013vt,Allegrini:2012kx}. The target is the computational interface between the building energy model, using EnergyPlus, and the urban energy model using CitySim. An overview of the larger scope is shown in Figure \ref{fig:UMEM} and the context of the coupling task is shown as the interface between the City Energy Simulation (CES) model and the Building Energy Simulation (BES) model.

@@

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between simulation engines at various scales. Much of the initial co-simulation work in the literature is at the subsystem and building-scales. Previous studies have analyzed strong and loose coupling of engines at this scale \citep{Trcka:2010cr,Wetter:2011kh}. Coupling of building-scale simulation with urban-scale computational fluid dynamics (CFD) is attempted for modeling natural ventilation \citep{Zhang:2013vx} and to improve energy prediction \citep{Bouyer:2011eha}. A comprehensive review of energy and airflow modeling of neighborhoods and university campuses was published that includes strategies aspects of coupling different types of models \citep{Srebric:2015gq}. EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program \citep{Yang:2012cr}. It was also coupled with simplified lumped parameter models in order to facilitate comparison with measured sensor data \citep{Martin:2015fj}. EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi} and urban weather generation \citep{Bueno:2013hh}. Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}.
% \subsection{Urban scale performance simulation}

\section{Methodology}\label{Methodology}
% Portions of the following methodology is developed in previous literature and is reiterated in this section in order to set the context for Section \ref{Implementation}. The previous published research is clearly outlined at the beginning of each subsection.

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.7]{figures/UMEM_Workflow}
\caption{Overview diagram of the coupling process including tools and outputs \citep{thomas2014multiscale}}
\label{fig:OverallWorkflowProcess}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.7]{figures/UMEM_FMU_Overview}
\caption{Simulation information exchange between CitySim and EnergyPlus using FMI \citep{thomas2014multiscale}}
\label{fig:FMUOverview}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1.0\textwidth]{figures/LWRCalc_Combined_V3}
  \caption{Comparison of the LWR components between a) Solo EnergyPlus and b) Coupled CitySim/EnergyPlus configuration \citep{Miller:2015vk}
  \label{combinedLWR}}
\end{figure}

\subsection{Work flow automation}
The coupling, simulation and co-simulation process is completely managed within a program called VisTrails. This tool empowers the coupling of various executable files and their connecting scripts in a graphical diagrams that enhances reproducibility and process automation \citep{Freire:2014tt}.

INSERT VISTRAILS GRAPHIC HERE

@@

The focus of the co-simulation process is that the performance of a targeted building is evaluated through solo and coupled methods. The HPI building on campus was chosen in this case study due to amount and quality of measured data available from the EMS for this building. HPI is a 2,610 sq. meter building that made up mostly of office space and classrooms. It also includes 400 sq. meter convenience store and coffee shop. The building is indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded red.

@@

\subsection{Model development}
In order to perform a co-simulation of the targeted buildings, initially a CitySim model of the campus is developed. Through the workflow automation process, this geometry was converted into an EnergyPlus input file as seen in Figure \ref{fig:HPIcampus}. The EnergyPlus input file is then used as an input to execute EnergyPlus solo and co-simulation processes for the purpose of simplified calibration, and then to understand the magnitude of difference between these simulation scenarios.
% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.

\begin{figure}[H]
\centering
\includegraphics[scale=0.2]{figures/HPI_Campus.png}
\caption{The HPI building modeled with OpenStudio for Sketchup}
\label{fig:HPIcampus}
\end{figure}

@@

The measured and simulated data from both the co-simulation and EnergyPlus solo simulation was compared in order to create a realistic scenario for comparison. The calibration process was undertaken through a series of steps such as including local weather conditions for the simulation period and adding custom lighting schedules and power densities extracted from the measured data. The models were calibrated to the summer season (May-September) for cooling and the winter season (Jan-April and October to December) for heating. This approach was taken as the data quality for the measurements were deemed most accurate during the appropriate seasons. Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the simulations after the tuning process. The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating. These metrics fall within the +/- 10\% and 30\% used in this case study for the purposes of partial calibration. The goal of calibration in this case is to simply bring the models to within a reasonable range of reality in order to bring more confidence to analysis of the discrepancies between the solo and co-simulation scenarios.
%Daily data was used to calculated goodness of fit to determine calibration success. 
%The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.

@@

After calibration, a comparison of co-simulation and solo EnergyPlus simulations is made. For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus. A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{hpi_energypluscooling}.

Figure \ref{fig:hpi_energyplusheating} illustates the difference in predicted heating energy consumption across the test year. A consistent offset exists across the time frame of days in January, the peak of the heating season. A more varied discrepancy across the heating months is noticed resulting and overall increase of heating prediction of 4.8\% due to co-simulation.

@@

@@

\subsection{Campus case study 2: EPFL Quartier Nord}
Quartier Nord is a whole new quarter of the École Polytechnique Fédérale de Lausanne (EPFL) campus located at its northwest corner. This complex includes a Convention Centre with an auditorium with a maximum capacity of 3000 (seated) people, housing for 516 students, retail and service areas and a hotel. As a public space, this ensemble is organized around a main plaza as seen in  Figure \ref{fig:quartier_nord_1}).

@@

Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information. A rendering of this model is seen in Figure \ref{fig:model_yang}.

@@

When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}.

@@

A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}.

@@

When focusing on solely on CitySim, a X\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}.

@@

A 30.8\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.

@@

Future work in using co-simulation models for buildings and campuses would more intensively utilize the model results in a practical implementation of retrofit scenarios or urban-scale energy systems research.

@@

The authors would like to acknowledge the ETH Z\"urich Campus Facilities Department and the EPFL Real Estate and Infrastructure Department. This research was funded by the Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale Energy Modeling (UMEM) project.
